---
title: "Thesis - part 1 exploratory"
author: "Thomas Lieber"
date: "24-3-2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())

```

#Library
```{r}
library("Amelia")
library("cowplot")
library("dtw")
#library("forecast")
library("ggplot2")
library("imputeTS")
library("openxlsx")
library('RColorBrewer')
library("readxl")
library("reshape2")
```

#Data importing hourly data
```{r}
#working directory
setwd("D:/master/Thesis/data")

#hourly data
temp1 = read.xlsx("Temperature_1.xlsx", sheet = 1, startRow = 1, colNames = TRUE)
temp2 = read.xlsx("Temperature_2.xlsx", sheet = 1, startRow = 1, colNames = TRUE)
temp3 = read.xlsx("Temperature_3.xlsx", sheet = 1, startRow = 1, colNames = TRUE)

#monthly data
monthly_raw = read.xlsx("Temperature_monthly.xlsx", sheet = 1, startRow = 1, colNames = TRUE)
```

#Data cleaning part 1
```{r}
temp_raw = rbind(temp1, temp2, temp3) #put all datasets together in one dataset
#set all -9999 to NA
ind_9999s = which(temp_raw == "-9999", arr.ind = T)
temp_raw[ind_9999s] = NA

#limit the dataset between 1853 January and 1963 December
ind_interval_years = which(temp_raw$YYYY > 1852 & temp_raw$YYYY < 1964)
temp_raw = temp_raw[ind_interval_years,]

#delete variables with the same info
temp_raw = temp_raw[,-which(colnames(temp_raw) %in% c("TA", "PA"))]

#change variable names to make them more understandable
new_names = c("temp", "airpressure", "wind_dir", "windforce", "windspeed")
colnames(temp_raw)[5:9] = new_names
```

#Missing per unique month
```{r}
months = as.character(temp_raw$M)
years_months = as.numeric(paste(temp_raw$YYYY, months, sep = ""))
temp_raw = cbind(years_months, temp_raw)

uniq_months = unique(years_months)
M = length(uniq_months)
missings_pm = matrix(0, M, 2)

#find the amount of missing values per month for air pressure and temperature.
for(i in 1:M){
  month_indice = which(temp_raw$years_months == uniq_months[i])
  month_ap = temp_raw$airpressure[month_indice]
  month_temp = temp_raw$temp[month_indice]

  missings_pm[i,1] = sum(is.na(month_ap))
  missings_pm[i,2] = sum(is.na(month_temp))
}


years_months_missing = which(missings_pm > 0)
```

#10th and 90th quantiles per month for temperature and air pressure
```{r}
var_names = c("temp", "airpressure")

CIs_m = matrix(0, 12, 4)

for(i in 1:12){
  month = temp_raw[which(temp_raw$M == i),]
  for(j in 1:2){
    variable = month[,var_names[j]]
    
    if(j == 1){
      CIs_m[i,1:2] = quantile(variable, probs = c(0.1, 0.9), na.rm = T, type = 8)
    }
    if(j == 2){
      CIs_m[i,3:4] = quantile(variable, probs = c(0.1, 0.9), na.rm = T, type = 8)
    }
  }
}
```

#Hours of and 90th percentile of temp and airpressure variables
```{r}
#Initialize matrix for temperature and air pressure variables.
feat_names = c("temp_min_hours",
                     "temp_max_hours", 
                     "temp_min", 
                     "temp_max", 
                     "temp_mean", 
                     "temp_sd", 
                     "airP_min_hours", 
                     "airP_max_hours", 
                     "airP_min", 
                     "airP_max",  
                     "airP_mean", 
                     "airP_sd")

feature_vars = matrix(0, length(uniq_months), length(feat_names))
colnames(feature_vars) = feat_names

#for every month per variable calculate summary measures 
for(i in 1:length(uniq_months)){

  month = temp_raw[which(temp_raw$years_months == uniq_months[i]),]
  M = month$M[1]

  for(j in 1:2){
    #j is air pressure or temperature.
    variable = month[,var_names[j]]

    if(j == 1){
      feature_vars[i,1] = length(variable[variable < CIs_m[M,1]])
      feature_vars[i,2] = length(variable[variable > CIs_m[M,2]])
      feature_vars[i,3] = min(variable, na.rm = T)
      feature_vars[i,4] = max(variable, na.rm = T)
      feature_vars[i,5] = mean(variable, na.rm = T)
      feature_vars[i,6] = sd(variable, na.rm = T)
      
    }
    if(j == 2){
      feature_vars[i,7] = length(variable[variable < CIs_m[M,3]])
      feature_vars[i,8] = length(variable[variable > CIs_m[M,4]])
      feature_vars[i,9] = min(variable, na.rm = T)
      feature_vars[i,10] = max(variable, na.rm = T)
      feature_vars[i,11] = mean(variable, na.rm = T)
      feature_vars[i,12] = sd(variable, na.rm = T)
    }
  }
}


airp_missing = which(missings_pm[,1] > 0)
temp_missing = which(missings_pm[,2] > 0)

feature_vars[airp_missing, (7:12)] = NA
feature_vars[temp_missing, (1:6)] = NA

feature_vars = as.data.frame(feature_vars)

length(unique(c(airp_missing, temp_missing))) #amount of months missing

is.inf <- function(x){
  x == Inf | x == -Inf
}

#no inf
colSums(apply(feature_vars, 2, is.inf), na.rm = T)
```

#Dry categorical
```{r}
#Find the unique values of the wind description variables.
values = unique(temp_raw$W1)
#find all characters which has the "droo" in it.
ind_droo = grepl("droo", values)
#select all values with "droo" in it
droog_values = values[ind_droo]
#Index of all values that do not refer to a dry weather description
not_droog = c(2,9,12,18,19,23:28,30,32,35,36,37,39,43,44,49,51,52,53,57)
#deselect all values that do not refer to a dry weather description
droog_values2 = droog_values[-not_droog]

#Set all missing values to NA and all droog values to 1
w1 = temp_raw$W1
na_ind = which(is.na(w1))
droog = (w1 %in% droog_values2) * 1
droog[na_ind] = NA
```

#Total dry hours per month
```{r}
droog_total = numeric(length(uniq_months))
#for every month calculate the sum of dry values
for(i in 1:length(uniq_months)){
  droog_total[i] = sum(droog[which(temp_raw$years_months == uniq_months[i])])
}
```

#Streak detect
```{r}
#function cacluates the maximum amount of 1 values in a row for a variable.
streak <- function(x){
  run = rle(x)
  ind = which(run$values == 1)
  return(max(run$lengths[ind]))
}
```

#Dry streak
```{r}
#calculate the maximum streak of dry hours per variable.
dry_streak = numeric(length(uniq_months))

for(i in 1:length(uniq_months)){
  dry_streak[i] = streak(droog[which(temp_raw$years_months == uniq_months[i])])
}

dry_streak[dry_streak == -Inf] = NA
```

#Wind direction
```{r}
#For every wind direction, calculate the amount of hours per month and save it into a variable.
direction_names = rownames(table(temp_raw$wind_dir))
w_direction_matrix = matrix(0, nrow = length(uniq_months), length(direction_names))
colnames(w_direction_matrix) = direction_names
count = 0

for(i in 1:length(uniq_months)){
  for(j in 1:length(direction_names)){
    month = temp_raw$wind_dir[which(temp_raw$years_months == uniq_months[i])]
    if(sum(is.na(month)) > 0){
      w_direction_matrix[i,] = NA
    }
    if(sum(is.na(month)) == 0){
      w_direction_matrix[i,direction_names[j]] = table(month)[direction_names[j]]
       if(!(direction_names[j] %in% month)){
          w_direction_matrix[i,direction_names[j]] = 0
        }
    }
  }
}
```

#Windforce
```{r}
#Split windforce into 3 categories: low, medium and high. Then, calculate per month the amount of hours per windforce category and save it into a variable.
wf = temp_raw$windforce
low_wf = c("stil", "bijna stil", "slappe koelte", "zacht", "zwak")
med_wf = c("matige koelte", "matig")
high_wf =  unique(wf)[!(unique(wf) %in% c(low_wf, med_wf))]

wf_matrix = matrix(0, length(uniq_months), 3)
wf_names = c("low_wf", "med_wf", "high_wf")
colnames(wf_matrix) = wf_names

for(i in 1:length(uniq_months)){
  month = wf[which(temp_raw$years_months == uniq_months[i])]
  
  wf_matrix[i,1] = sum(month %in% low_wf)
  wf_matrix[i,2] = sum(month %in% med_wf)
  wf_matrix[i,3] = sum(month %in% high_wf)
  if(sum(is.na(month)) > 0){
    wf_matrix[i,] = NA
  }
}
```

#Feature engineered variables together
```{r}
#put all the feature engineered variables together.
new_y_m = matrix(NA, length(uniq_months), 2)
for(i in 1:length(uniq_months)){
  row = as.character(uniq_months[i])
  splitup = strsplit(row, "")
  new_y_m[i,1] = paste(splitup[[1]][1:4], sep = "", collapse = "")
  new_y_m[i,2] = paste(splitup[[1]][5:length(splitup[[1]])], sep = "", collapse = "")
}


feature_vars_all = data.frame(years_months = as.numeric(uniq_months),
                              year = as.numeric(new_y_m[,1]), 
                              month = as.numeric(new_y_m[,2]), 
                              feature_vars, 
                              dry_total = droog_total, 
                              dry_streak = dry_streak, 
                              w_direction_matrix, 
                              wf_matrix)
```

#Summary stats
```{r}
#For every variable, calcuate summary statistics and save it into table format for Latex.
summary_function_num <- function(column){
  #places various summary measure (mean, sd etc) of numeric variables into a vector
  rown = c("min", "max", "mean", "sd",  "median", "NA %")
  vec = numeric(length(rown))
  names(vec) = rown
  vec[1] = min(column, na.rm = TRUE)
  vec[2] = max(column, na.rm = TRUE)
  vec[3] = mean(column, na.rm = TRUE)
  vec[4] = sd(column, na.rm = TRUE)
  vec[5] = median(column, na.rm = TRUE)
  vec[6] = sum(is.na(column)) / length(column) * 100
  vec = round(vec,2)
  return(vec)
}

titles = c("Hours >10th percentile temperature",
           "Hours <90th percentile temperature",
           "Min. temperature",
           "Max. temperature",
           "Mean temperature",
           "Std. temperature ",
           "Hours >10th percentile air pressure",
           "Hours <90th percentile air pressure",
           "Min. air pressure",
           "Max. air pressure",
           "Mean air pressure",
           "Std. air pressure",
           "Dry hours",
           "Max. streak dry hours",
           "Hours of north wind",
           "Hours of north-east wind",
           "Hours of north-west wind",
           "Hours of east wind",
           "Hours of west wind",
           "Hours of south wind",
           "Hours of south-east wind",
           "Hours of south-west wind",
           "Hours of low windspeed",
           "Hours of medium windspeed",
           "Hours of high windspeed")


y_labs = character(25)
y_labs[c(1:2,7:8,13:25)] = "Hours"
y_labs[3:6] = "Temp. Celcius"
y_labs[9:12] = "hPa"

df = apply(feature_vars_all[,-(1:3)], 2, summary_function_num)
df[6,] = paste(df[6,], "%", sep = "")

df2 = data.frame(colnames(df), t(df))
names_df2 = c("Variable name", 'Unit of measure', "Min.", "Max.", "Mean", "Sd", "Median", "NA %")

latex_line <- function(row){
  latex_row = paste(as.character(row), collapse = "&")
  add = " \\\ hline"
  latex_row = paste(latex_row, add)
  return(latex_row)
}

df3 = rbind(names_df2,  cbind(df2[,1], cbind(y_labs, df2[,2:7])))

df3[-1,1] = titles

output_latex = apply(df3, 1, latex_line)
#write.table(output_latex, file="summary_stats_feature.txt", row.names=FALSE, col.names=FALSE)

df = apply(monthly_raw[,-(1:2)], 2, summary_function_num)
df[6,] = paste(df[6,], "%", sep = "")

df2 = data.frame(colnames(df), t(df))
names_df2 = c("Variable name", 'Unit of measure', "Min.", "Max.", "Mean", "Sd", "Median", "NA %")

units = c("mm", "mm", "% humidity", "% humidity")

df3 = rbind(names_df2,  cbind(df2[,1], cbind(units, df2[,2:7])))

output_latex = apply(df3, 1, latex_line)
#write.table(output_latex, file="summary_stats_monthly.txt", row.names=FALSE, col.names=FALSE)
```

#Legend for seasonality plots
```{r}
#Make a vector which contains colors that slowly change from cyan to darkblue
colfunc <- colorRampPalette(c("cyan", "darkblue"))
gradient_year = colfunc(length(uniq_months))
df = data.frame(seq(1853, 1964, 1/12)[-1333], rep(1,1332), gradient_year)

legend = ggplot(data = df, aes(x = df[,1], y = df[,2])) +
  geom_point(color = df[,3], size = 25) +
  xlab("") +
  ylab("") +
  theme_classic() +
  scale_x_continuous(name = "Years",
                   limits = c(1853, 1964)) +
  ggtitle("Legend Seasonality plots") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title = element_text(family = "serif", size = 20),
        line = element_blank(),
        axis.text.x = element_text(size = 25),
        plot.title = element_text(hjust = 0.5, family = "serif", size = 35),
        axis.title.x = element_text(size = 25))
legend_name = "legend_seasonality.pdf"
print(legend)
#ggsave(legend_name, plot = legend, device = "pdf")
```

#Seasonality plots
```{r}
#Create seasonality plots for each variable.

feature_vars_all_plot = cbind(feature_vars_all, gradient_year)

y_labs = character(25)
y_labs[c(1:2,7:8,13:25)] = "Hours"
y_labs[3:6] = "Temp. Celcius"
y_labs[9:12] = "hPa"

titles = c("10th percentile temperature",
           "90th percentile temperature",
           "Min. temperature",
           "Max. temperature",
           "Mean temperature",
           "Std. temperature",
           "10th percentile Air pressure",
           "90th percentile Air pressure",
           "Min. Air pressure",
           "Max. Air pressure",
           "Mean Air pressure",
           "Std. Air pressure",
           "Number of dry hours",
           "Largest streak of dry hours",
           "Hours of north wind",
           "Hours of north-east wind",
           "Hours of north-west wind",
           "Hours of east wind",
           "Hours of west wind",
           "Hours of south wind",
           "Hours of south-east wind",
           "Hours of south-west wind",
           "Hours of low windspeed",
           "Hours of medium windspeed",
           "Hours of high windspeed")

titles_plot  = paste("seasonplot_", gsub(" ", "_", titles), '.pdf', sep = '')


for(i in 4:ncol(feature_vars_all)){
  plot = ggplot(data=feature_vars_all_plot, aes(x=month, y=feature_vars_all_plot[,i], group=year, col = gradient_year)) +
    geom_line(color=gradient_year) +
    geom_point(color = gradient_year) + 
    theme(legend.position = "none") +
    ggtitle(titles[i-3]) + 
    scale_x_continuous(breaks = 1:12) +
    xlab("Month") +
    ylab(y_labs[i-3]) +
    theme(axis.title = element_text(family = "serif", size = 35),
          title = element_text(family = "serif", size = 35),
          plot.title = element_text(hjust = 0.5, size = 35),
          axis.text = element_text(size = 30))
  #ggsave(titles_plot[i-3], plot = plot, device = "png")
}
print(plot)


#monthly seasonal plot 2

#monthly starts later so gradient_year needs to be started at the right indice
ind_monthly = which(uniq_months == 18911)
gradient_year2 = gradient_year[ind_monthly:1332]
monthly_raw_plot = cbind(monthly_raw, gradient_year2)

y_labs2 = character(4)
y_labs2[1:2] = "mm"
y_labs2[3:4] = "% Humidity"

titles2 = c("Percipitation total",
           "Percipitation max",
           "Relative humidity mean",
           "Relative humdity at 8am")

titles2_plot  = paste("seasonplot_", gsub(" ", "_", titles2), '.pdf', sep = '')


for(i in 3:ncol(monthly_raw)){
  plot = ggplot(data=monthly_raw_plot, aes(x=month, y=monthly_raw_plot[,i], group=year, col = gradient_year2)) +
    geom_line(color=gradient_year2) +
    geom_point(color = gradient_year2) + 
    theme(legend.position = "none") +
    ggtitle(titles2[i-2]) + 
    scale_x_continuous(breaks = 1:12) +
    xlab("Month") +
    ylab(y_labs2[i-2]) +
    theme(axis.title = element_text(family = "serif", size = 35),
          title = element_text(family = "serif", size = 35),
          plot.title = element_text(hjust = 0.5, size = 35),
          axis.text = element_text(size = 30))

  #ggsave(titles2_plot[i-2], plot = plot, device = "png")
}
plot
```

#Kernel density cv and/or histogram
```{r}
cols = rainbow(length(y_labs), s=.6, v=.9)[sample(1:length(y_labs),length(y_labs))]
titles_plot_hist  = paste("hist_", gsub(" ", "_", titles), '.pdf', sep = '')



for(i in 4:ncol(feature_vars_all)){
  plot = ggplot(feature_vars_all, aes(x= (feature_vars_all)[,i])) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white", alpha = .1) +
    geom_density(alpha=.2, fill = cols[i-3]) +
    xlab(y_labs[i-3]) +
    ggtitle(titles[i-3]) +
    theme(axis.title = element_text(family = "serif", size = 35),
          title = element_text(family = "serif", size = 35),
          plot.title = element_text(hjust = 0.5, size = 35),
          axis.text = element_text(size = 30))
  #ggsave(titles_plot_hist[i-3], plot = plot, device = "pdf")
}
plot

#Kernel density cv and/or histogram monthly part 2

cols = rainbow(length(y_labs2), s=.6, v=.9)[sample(1:length(y_labs2),length(y_labs2))]
titles2_plot_hist  = paste("hist_", gsub(" ", "_", titles2), '.pdf', sep = '')


for(i in 3:ncol(monthly_raw)){
  plot = ggplot(monthly_raw_plot, aes(x= (monthly_raw_plot)[,i])) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white", alpha = .1) +
    geom_density(alpha=.2, fill = cols[i-2]) +
    xlab(y_labs2[i-2]) +
    ggtitle(titles2[i-2]) +
    theme(axis.title = element_text(family = "serif", size = 35),
          title = element_text(family = "serif", size = 35),
          plot.title = element_text(hjust = 0.5, size = 35),
          axis.text = element_text(size = 30))
  #ggsave(titles2_plot_hist[i-2], plot = plot, device = "pdf")
}
```

#Time series plots
```{r}
titles_plot_ts  = paste("timeseries_", gsub(" ", "_", titles), '.pdf', sep = '')
cols = rainbow(length(y_labs), s=.6, v=.9)[sample(1:length(y_labs),length(y_labs))]
ind_ts = seq(1853, 1964, 1/12)
ind_ts = ind_ts[-1333]

for(i in 4:ncol(feature_vars_all)){
  plot = ggplot(data=feature_vars_all_plot, aes(x=ind_ts, y=feature_vars_all[,i])) +
    geom_line(color=cols[i-3]) +
    #geom_point(aes(color=cols[i-3])) + 
    theme(legend.position = "none") +
    ggtitle(titles[i-3]) + 
    xlab("Months") +
    ylab(y_labs[i-3]) +
    theme(axis.title = element_text(family = "serif", size = 35),
          title = element_text(family = "serif", size = 35),
          plot.title = element_text(hjust = 0.5, size = 45),
          axis.text = element_text(size = 30))
  print(plot)
  #ggsave(titles_plot_ts[i-3], plot = plot, device = "pdf", width = 12, height = 8)
}

#timeseries plots 2 

cols = rainbow(length(y_labs2), s=.6, v=.9)[sample(1:length(y_labs2),length(y_labs2))]

titles2_plot_ts  = paste("timeseries_", gsub(" ", "_", titles2), '.pdf', sep = '')

ind_ts2 = seq(1890, 1963, 1/12)
ind_ts2 = ind_ts2[-877]

for(i in 3:ncol(monthly_raw)){
  plot = ggplot(data=monthly_raw_plot, aes(x=ind_ts2, y=monthly_raw_plot[,i])) +
    geom_line(color=cols[i-2]) +
    theme(legend.position = "none") +
    ggtitle(titles2[i-2]) + 
    xlab("Months") +
    ylab(y_labs2[i-2])  +
    theme(axis.title = element_text(family = "serif", size = 35),
          title = element_text(family = "serif", size = 35),
          plot.title = element_text(hjust = 0.5, size = 45),
          axis.text = element_text(size = 30))

  print(plot)
  #ggsave(titles2_plot_ts[i-2], plot = plot, device = "pdf", width = 12, height = 8)
}
```



#PACF and ACF
```{r}
acf_titles = paste("acf_", gsub(" ", "_", titles), '.pdf', sep = '')
pacf_titles = paste("pacf_", gsub(" ", "_", titles), '.pdf', sep = '')

for(i in 4:ncol(feature_vars_all)){
  variable = ts(feature_vars_all[,i], frequency = 12)
  
  plot1 = ggAcf(variable, lag.max = 12, type = "partial") +
    theme(axis.title = element_text(family = "serif", size = 35),
          title = element_text(family = "serif", size = 35),
          plot.title = element_text(hjust = 0.5, size = 35),
          axis.text = element_text(size = 30)) +
    xlab("Month") +
    ylim(c(-1,1)) +
    scale_x_continuous(breaks = 1:12) +
    ggtitle(titles[i-3])
  
  plot2 = ggAcf(variable, lag.max = 12, type = "correlation") +
    theme(axis.title = element_text(family = "serif", size = 35),
          title = element_text(family = "serif", size = 35),
          plot.title = element_text(hjust = 0.5, size = 35),
          axis.text = element_text(size = 30)) +
    xlab("Month") +
    ylim(c(-1,1)) +
    scale_x_continuous(breaks = 1:12) +
    ggtitle(titles[i-3])
  
  #ggsave(acf_titles[i-3], plot = plot1, device = "pdf")
  #ggsave(pacf_titles[i-3], plot = plot2, device = "pdf")
}


acf_titles2 = paste("acf_", gsub(" ", "_", titles2), '.pdf', sep = '')
pacf_titles2 = paste("pacf_", gsub(" ", "_", titles2), '.pdf', sep = '')



for(i in 3:ncol(monthly_raw)){
  variable = ts(monthly_raw[,i], frequency = 12)
  
  plot1 = ggAcf(variable, lag.max = 12, type = "partial") +
    theme(axis.title = element_text(family = "serif", size = 35),
          title = element_text(family = "serif", size = 35),
          plot.title = element_text(hjust = 0.5, size = 35),
          axis.text = element_text(size = 30)) +
    xlab("Month") +
    ylim(c(-1,1)) +
    scale_x_continuous(breaks = 1:12) +
    ggtitle(titles2[i-2])
  
  plot2 = ggAcf(variable, lag.max = 12, type = "correlation") +
    theme(axis.title = element_text(family = "serif", size = 35),
          title = element_text(family = "serif", size = 35),
          plot.title = element_text(hjust = 0.5, size = 35),
          axis.text = element_text(size = 30)) +
    xlab("Month") +
    ylim(c(-1,1)) +
    scale_x_continuous(breaks = 1:12) +
    ggtitle(titles2[i-2])
  
  #ggsave(acf_titles2[i-2], plot = plot1, device = "pdf")
  #ggsave(pacf_titles2[i-2], plot = plot2, device = "pdf")
}
```

#Correlation matrices
```{r}
inds = seq(1,1332,1332/4)

interval_years = character(4)
years = feature_vars_all$year
interval_years[1] = paste(years[inds[1]], " - ", years[inds[2]])
interval_years[2] = paste(years[inds[2]], " - ", years[inds[3]])
interval_years[3] = paste(years[inds[3]], " - ", years[inds[4]])
interval_years[4] = paste(years[inds[4]], " - ", years[1332])

feature_vars_all$percip_total = NA
feature_vars_all$percip_max = NA
feature_vars_all$humid_mean = NA
feature_vars_all$humid_8am = NA

feature_vars_all$percip_total[ind_monthly:1332] = monthly_raw$precipitation_total
feature_vars_all$percip_max[ind_monthly:1332] = monthly_raw$precipitation_max
feature_vars_all$humid_mean[ind_monthly:1332] = monthly_raw$rel_hum_mean
feature_vars_all$humid_8am[ind_monthly:1332] = monthly_raw$rel_hum_8h


cormat1 = cor(feature_vars_all[(inds[1]:inds[2]),-c(1:3,32,31,30,29)], use = "pairwise.complete")
cormat2 = cor(feature_vars_all[(inds[2]:inds[3]),-(1:3)], use = "pairwise.complete")
cormat3 = cor(feature_vars_all[(inds[3]:inds[4]),-(1:3)], use = "pairwise.complete")
cormat4 = cor(feature_vars_all[(inds[4]:1332),-(1:3)], use = "pairwise.complete")

cormats = list(cormat1, cormat2, cormat3, cormat4)
cormats_name = c("cormat1.pdf", "cormat2.pdf", "cormat3.pdf", "cormat4.pdf")

# Get lower triangle of the correlation matrix, we use upper for what you wanted
get_lower_tri<-function(cormat){
  cormat[upper.tri(cormat)] <- NA
  return(cormat)
}
# Get upper triangle of the correlation matrix
get_upper_tri <- function(cormat){
  cormat[lower.tri(cormat)]<- NA
  return(cormat)
}

for(i in 1:4){
  upper_tri <- get_upper_tri(cormats[[i]])
  melted_cormat <- melt(upper_tri, na.rm = TRUE)
  ggheatmap <- ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson correlation") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 12, hjust = 1))+
  coord_fixed()

  plot = ggheatmap + 
  theme(legend.justification = c(1, 0),
        legend.position = c(0.3, 0.5),
        axis.title = element_blank()) +
  guides(fill = guide_colorbar(title.position = "top", title.hjust = 0.5))
  print(plot)
 #ggsave(cormats_name[i], plot = plot, device = "pdf")
}
```

#Latex output 
```{r}
output_grid <- function(name_vec1){
  name_vec = name_vec1
  if(length(name_vec1) < 20){
    name_vec = character(20)
    name_vec[1:length(name_vec1)] = name_vec1
    name_vec[(length(name_vec1)+1):20] = "x.pdf"
  }
  
  output_vec = character(27)
  output_vec[1] = "*begin{figure}[H]"
  output_vec[c(6,11,16,21)] = "**[*smallskipamount]"
  output_vec[26] = "*caption{some}*label{fig:foobar}"
  output_vec[27] = "*end{figure}"
  inds = which(!(1:27 %in% c(1,6,11,16,21,26,27)))
  
  for(i in 1:length(inds)){
    output_vec[inds[i]] = paste("*includegraphics[width=.24*textwidth]{", name_vec[i], "}*hfill", sep = "")
  }
  return(output_vec)
}

plots1_season = output_grid(titles_plot[1:20])
plots2_season = output_grid(c(titles_plot[21:length(titles_plot)], titles2_plot))

plots1_hist = output_grid(titles_plot_hist[1:20])
plots2_hist = output_grid(c(titles_plot_hist[21:length(titles_plot_hist)], titles2_plot_hist))

plots1_acf = output_grid(acf_titles[1:20])
plots2_acf = output_grid(c(acf_titles[21:length(acf_titles)], acf_titles2))

plots1_pacf = output_grid(pacf_titles[1:20])
plots2_pacf = output_grid(c(pacf_titles[21:length(pacf_titles)], pacf_titles2))

plots1_ts = output_grid(titles_plot_ts[1:20])
plots2_ts = output_grid(c(titles_plot_ts[21:length(titles_plot_ts)], titles2_plot_ts))


table_names = c("plots1_season",
                "plots2_season",
                "plots1_hist",
                "plots2_hist",
                "plots1_acf",
                "plots2_acf",
                "plots1_pacf",
                "plots2_pacf",
                "plots1_ts",
                "plots2_ts")

table_names = paste(table_names, ".txt", sep = "")

table_names_list = list(plots1_season,
                plots2_season,
                plots1_hist,
                plots2_hist,
                plots1_acf,
                plots2_acf,
                plots1_pacf,
                plots2_pacf,
                plots1_ts,
                plots2_ts)

for(i in 1:length(table_names)){
  write.table(table_names_list[[i]], file=table_names[i], row.names=FALSE, col.names=FALSE)
}
```

#write csv
```{r}
path = "D:\\master\\Thesis\\data\\cleaned_data.csv"
write.csv(feature_vars_all, path, row.names = FALSE, sep = ';')
```


