---
title: "Multivariate"
author: "Thomas Lieber"
date: "12-6-2021"
output: html_document
---

```{r}
rm(list=ls())
```

#Library
```{r}
library(ConsensusClusterPlus)
library(caret)
library(dbscan)
library(ggplot2)
library(MASS)
library(mgcv)
library(neatmaps)
library(randomForest)
library(reshape2)
library(Rtsne)
library(vegan)
```

#Data
```{r}
#working directory
setwd("D:/master/Thesis/data")
data = as.data.frame(read.csv("imputed_data.csv"))
```
#set data
```{r}
data1 = data[,-c(29:32)] #Remove percipitation and humidity variables as not all observations are available here.

standardize <- function(x){(x - mean(x))/sd(x)}

data1_z = as.data.frame(apply(data1[,-c(1:3,26:28)], 2, standardize)) #Remove year, year_months and months from the to be standardized. Also remove wind strength variables as they are not homogenous enough to be used for the analyses.
```

#Distance euclidean
```{r}
eu_data1 = dist(data1_z) #Transform the data to a euclidean distance matrix.
```


#consensus cluster
```{r}
set.seed(2020)
consensus = ConsensusClusterPlus(eu_data1, maxK = 16, reps = 50, clusterAlg = "pam", seed = 2020)
```

#PAC function
```{r}
PAC2 <- function(cons_r){
  Kvec = 2:length(cons_r)
  x1 = 0.1; x2 = 0.9 # threshold defining the intermediate sub-interval
  PAC = rep(NA,length(Kvec)) 
  names(PAC) = paste("K=",Kvec,sep="") # from 2 to maxK
  for(i in Kvec){
    M = cons_r[[i]]$consensusMatrix
    Fn = ecdf(M[lower.tri(M)])
    PAC[i-1] = Fn(x2) - Fn(x1)
  }#end for iw\
  return(PAC)
}


abs(pac_consensus[1:15] - pac_consensus[2:16])
pac_df = data.frame(PAC = PAC2(consensus), K = 2:16)
```
#clustering PAC plot
```{r}
plot = ggplot(data=pac_df, aes(x=K, y=PAC)) +
  geom_point(size = 4) +
  geom_line() +
  #scale_x_discrete(labels = factor(means$V1)) +
  ggtitle("PAC plot") +
  xlab("K") +
  ylab("PAC") +
  ylim(c(0,0.5)) +
  #theme_bw()+
  theme_bw() +
  theme(axis.text.x = element_text(family = "serif", size = 20), 
        plot.title = element_text(hjust = 0.5, family = "serif", size = 30),
        axis.text.y = element_text(family = "serif", size = 25),
        legend.position = "none", 
        axis.title.y = element_text(family = "serif", size = 25),
        axis.title.x = element_text(family = "serif", size = 25))

plot
```

#mean absolute difference and pairwise difference function
```{r}


titles = c("year_months",
           "Year",
           "Month",
           "Hours >10th percentile temperature",
           "Hours <90th percentile temperature",
           "Min. temperature",
           "Max. temperature",
           "Mean temperature",
           "Std. temperature ",
           "Hours >10th percentile air pressure",
           "Hours <90th percentile air pressure",
           "Min. air pressure",
           "Max. air pressure",
           "Mean air pressure",
           "Std. air pressure",
           "Dry hours",
           "Max. streak dry hours",
           "Hours of north wind",
           "Hours of north-east wind",
           "Hours of north-west wind",
           "Hours of east wind",
           "Hours of west wind",
           "Hours of south wind",
           "Hours of south-east wind",
           "Hours of south-west wind",
           "Hours of low windspeed",
           "Hours of medium windspeed",
           "Hours of high windspeed",
           "classess")


k = 12

z_data1 = as.data.frame(apply(data1, 2, standardize))


classes = consensus[[k]]$consensusClass
table(classes)

means = as.data.frame(matrix(0, ncol(z_data1), 4))

#means[,1] = colnames(z_data1)
means[,1] = titles

mean_per_class <- function(x, classes){
    mean_pc = matrix(0, length(unique(classes)), 2)
    for(i in unique(classes)){
      mean_pc[i,1] = mean(x[which(classes == i)])
      mean_pc[i,2] = median(x[which(classes == i)])
    }
    mad = abs(max(mean_pc[,1]) - min(mean_pc[,1]))
    med = max(mean_pc[,2]) - min(mean_pc[,2])
    #sds = sd(mean_pc)
    #sds = mean_absolute_difference(mean_pc)
    sds = mean(dist(mean_pc[,1]))#pairwise distances mean
    return(c(mad, sds, med))
}

for(j in 1:nrow(means)){

  var = z_data1[,j]
  
  
  means[j,2:4] = mean_per_class(var, classes)
}
means = means[order(means[,2]),]
means$x = 1:nrow(means)
means = means[-c(7,29),] #delete years_months, time and classes
```

#mean difference plot
```{r}
plot = ggplot(data=means[-27,], aes(x=reorder(V1,V2), y=V2)) +
  geom_point(shape = 18, size = 5) +
  scale_x_discrete(labels = factor(means$V1)) +
  ggtitle("Maximium mean difference between clusters") + 
  ylab("Max standardized mean difference") + 
  xlab("") +
  ylim(c(0,3.5)) +
  coord_flip()+
  theme_bw() +
  theme(
    axis.title = element_text(vjust = 0.5, family = "serif", size = 25),
   axis.text.x = element_text( vjust = 0.5, family = "serif", size = 25),
        plot.title = element_text(hjust = 0.5, family = "serif", size = 25),
        axis.text.y = element_text(family = "serif", size = 25),
        legend.position = "none", 
 
        axis.title.y = element_text(family = "serif", size = 25)
    )

plot
```

#pairwise distance difference plot
```{r}
means = means[order(means[,4]),]
plot = ggplot(data=means[-27,], aes(x=reorder(V1,V3), y=V3)) +
  #geom_line() +
  geom_point(shape = 18, size = 5) +
  ylim(c(0,1.5)) +
  scale_x_discrete(labels = factor(means$V1)) +
  ggtitle("Mean pairwise distance between clusters") +
  ylab("Standardize mean pairwise distance") +
  xlab("") +
  coord_flip()+
  theme_bw() + 
  theme(
    axis.title = element_text(vjust = 0.5, family = "serif", size = 25),
   axis.text.x = element_text( vjust = 0.5, family = "serif", size = 25),
        plot.title = element_text(hjust = 0.5, family = "serif", size = 25),
        axis.text.y = element_text(family = "serif", size = 25),
        legend.position = "none", 
 
        axis.title.y = element_text(family = "serif", size = 25)
    )


plot

```

#consensus 6 time periods
```{r}
ind = round(seq(0, 111, 111/8)[4:9] * 12)
cons_list = list()
set.seed(2020)
i = 1
time = numeric(6)

for(i in 1:length(ind)){
  ptm = proc.time()
  print(i)
  interval = (ind[i]-500):ind[i]
  eu_data_part = dist(data1_z[interval,])
cons_list [[i]] = consensus_part = ConsensusClusterPlus(eu_data_part, maxK = 16, reps = 50, clusterAlg = "pam", seed = 2020)
  time[i] = (proc.time() - ptm)[1]
}
```



#difference per min and max standardize value of each cluster per variable plotted on the x axis 
```{r}
#difference per min and max standardize value of each cluster per variable plotted on the x axis 
k = 12

z_data1 = as.data.frame(apply(data1[,-c(1,29)], 2, standardize))

classes = consensus[[k]]$consensusClass
table(classes)

means = as.data.frame(matrix(0, ncol(z_data1), 4))
means[,1] = titles[-c(1,29)] #colnames(z_data1)


means_list = list()

for(i in 1:6){
  classes = cons_list[[i]][[k]]$consensusClass
  print(i)
  interval = (ind[i]-500):ind[i]
  interval_s = interval[!(interval %in% c(371))]
  print(table(classes))
  for(j in 1:nrow(means)){
    

  var = z_data1[interval_s,j]
  
  
  means[j,2:4] = mean_per_class(var, classes)
  }
  means = means[order(means[,2]),]
  means$x = 1:nrow(means)
  means_list[[i]] = means
}

end = round(1853 + 1/12 * ind)
start = round(1853 + 1/12 * (ind- 500)) 

PAC_matrix = NULL

for(i in 1:6){
  time_period = paste(start[i], end[i], sep = " - ")
  PAC_matrix = rbind(PAC_matrix, cbind(PAC2(cons_list[[i]]), 1:16, rep(time_period, 16)))
}
pac_df2 = as.data.frame(PAC_matrix)
pac_df2$V1 = as.numeric(pac_df2$V1)
pac_df2$V2 = as.numeric(pac_df2$V2)

```
#plots PAC
```{r}
#clustering PAC plot

colfunc <- colorRampPalette(c("cyan", "darkblue"))
colors_year_periods = colfunc(6)

plot = ggplot(data=pac_df2, aes(x=V2, y=V1, col = V3)) +
  geom_point(size = 4) +
  geom_line() +
  #scale_x_discrete(labels = factor(means$V1)) +
  ggtitle("PAC plot seperate time periods") +
  xlab("K") +
  ylab("PAC") +
  ylim(c(0,0.8)) +
  theme_bw()+
  theme(axis.text.x = element_text(family = "serif", size = 20), 
        plot.title = element_text(hjust = 0.5, family = "serif", size = 30),
        axis.text.y = element_text(family = "serif", size = 25),
        #legend.position = "none", 
        axis.title.y = element_text(family = "serif", size = 25),
        axis.title.x = element_text(family = "serif", size = 25),
        legend.key.size = unit(2, 'cm'),
        legend.title = element_text(family = "serif", size = 20),
        legend.text = element_text(family = "serif", size = 20))


plot+ labs(color='Time periods') + scale_color_manual(values=colors_year_periods)



```




#plots
```{r}
for(i in 1:6){
  plot = ggplot(data=means_list[[i]], aes(x=reorder(V1,V2), y=V2)) +
  #geom_line() +
  geom_point(shape = 18, size = 5) +
  ggtitle(paste("Maximium mean difference between classes set ", i, sep = "")) + 
  ylab("Max standardized mean difference") + 
  xlab("") +
  ylim(c(0,4)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, family = "serif", size = 15), 
        plot.title = element_text(hjust = 0.5, family = "serif", size = 20),
        axis.text.y = element_text(family = "serif", size = 15),
        legend.position = "none", axis.title.x = element_blank(), 
        axis.title.y = element_text(family = "serif", size = 15))
  print(plot)
}
```


#plots all sets maxmeandiff
```{r}
all_means = NULL



for(i in 1:6){
  time_period = paste(start[i], end[i], sep = " - ")
  all_means = rbind(all_means, cbind(means_list[[i]], rep(time_period, nrow(means))))
  #all_means = rbind(all_means, cbind(means_list[[i]], rep(i, nrow(means))))
}

#all_means[,6] = as.character(all_means[,6])

plot = ggplot(data=all_means, aes(x=V1, y=V2, col = all_means[,6])) +
  #geom_line() +
  geom_point(shape = 18, size = 5) +
  ggtitle(paste("Maximium mean difference between all datasets ",  sep = "")) + 
  ylab("Max standardized mean difference") + 
  xlab("") +
  ylim(c(0,4)) +
  coord_flip()+
  theme_bw() +
  theme(axis.text.x = element_text(family = "serif", size = 20), 
        plot.title = element_text(hjust = 0.5, family = "serif", size = 20),
        axis.text.y = element_text(family = "serif", size = 15),
        #legend.position = "none", 
        axis.title.x = element_text(family = "serif", size = 25), 
        axis.title.y = element_text(family = "serif", size = 15),
        legend.key.size = unit(2, 'cm'),
        legend.title = element_text(family = "serif", size = 20),
        legend.text = element_text(family = "serif", size = 20))

print(plot+ labs(color='Time periods') + scale_color_manual(values=colors_year_periods)  )
```


#plots all sets pairs
```{r}
plot = ggplot(data=all_means, aes(x=V1, y=V3, col = all_means[,6],)) +
  #geom_line() +
  geom_point(shape = 18, size = 5) +
  ggtitle(paste("Pairwise mean difference between all datasets ",  sep = "")) + 
  ylab("Pairwise standardized mean difference") + 
  xlab("") +
  ylim(c(0,1.5)) +
  coord_flip()+
  
  theme(axis.text.x = element_text(family = "serif", size = 25), 
        plot.title = element_text(hjust = 0.5, family = "serif", size = 20),
        axis.text.y = element_text(family = "serif", size = 15),
        #legend.position = "none", 
        axis.title.x = element_text(family = "serif", size = 25), 
        axis.title.y = element_text(family = "serif", size = 15),
        legend.key.size = unit(2, 'cm'),
        legend.title = element_text(family = "serif", size = 20),
        legend.text = element_text(family = "serif", size = 20))

print(plot+ labs(color='Time periods') + scale_color_manual(values=colors_year_periods)  )
```


#Functions for saving the errors over time
```{r}

inds <- function(x){
  c(start_point + x - 1, (2*start_point)+x - 1)
}

class_error <- function(actual, pred){
  acc = numeric(12)
  for(i in 1:12){
    acc[i] = mean(actual[actual == i] == pred[actual == i], na.rm = T)
  }
  return(acc)
}

int_error <- function(pred, actual){
  m_pred = matrix(rep(1:12, length(pred)), nrow = length(pred), byrow = T)
  m_pred = abs(m_pred - pred)[actual]
  return(m_pred)
}

error_sym <- function(x_pred, x_actual){
   abs(((x_actual - x_pred + 6) %% 12) - 6)
}

```


sym error func:
$f(y , \hat{y}) = |((y - \hat{y} + 6)\text{ }mod \text{ } 12) - 6|$


#LDA
```{r}
month_names = c("January",
                 "February",
                 "March",
                 "April",
                 "May",
                 "June",
                 "July",
                 "August",
                 "September",
                 "October",
                 "November",
                 "December")

set.seed(20); palette = distinctColorPalette(12)#; pie(rep(1,12), col = palette)

lda_data = cbind(data1$month, data1[,-c(1:3,26:28)])
colnames(lda_data)[1] = "month"
lda_data$month = factor(lda_data$month)
model = lda(month ~ ., data = lda_data)



lda.data <- cbind(lda_data, predict(model)$x)
lda.data$month = as.character(lda.data$month)
group_col = character(nrow(lda.data))
for(i in 1:12){
  lda.data$month[which(lda.data$month == i)] = month_names[i]
  group_col[lda.data$month == month_names[i]] = palette[i]
}
lda.data$month = factor(lda.data$month, levels = month_names)

plot = ggplot(lda.data, aes(LD1, LD2, col = month)) +
  geom_point(size = 2) +
  theme(
  legend.title = element_text(size = 14),
  legend.text = element_text(size = 15),
  legend.key.size = unit(1, "cm") 
  )

plot + guides(colour = guide_legend(override.aes = list(size=7))) + labs(color='Months') + scale_color_manual(values=group_col) 

```

#lda 2 
```{r}

years = 40
start_point = (12 * years) + 1


ind = round(seq(0, 111, 111/8)[4:9] * 12)
cons_list = list()
set.seed(2020)



lda_data_main = lda_data[1:(ind[1]),-24]

lda_m = lda(month ~ ., data = lda_data_main)


lda.data <- cbind(lda_data, predict(model)$x)
lda.data$month = as.character(lda.data$month)
group_col = character(nrow(lda_data_main))




lda.data <- cbind(lda_data_main, predict(lda_m)$x)

lda.data$month = as.character(lda.data$month)
group_col = character(nrow(lda.data))
for(i in 1:12){
  lda.data$month[which(lda.data$month == i)] = month_names[i]
  group_col[lda.data$month == month_names[i]] = palette[i]
}
lda.data$month = factor(lda.data$month, levels = month_names)

plot = ggplot(lda.data, aes(LD1, LD2, col = month)) +
  xlab("LD1")+
  ylab("LD2")+
  ggtitle("LDA components plot") + 
  geom_point(size = 2) +
  theme_bw() +
  theme(
  plot.title = element_text(hjust = 0.5, family = "serif", size = 20),
  legend.title = element_text(size = 20, family = "serif"),
  legend.text = element_text(size = 20, family = "serif"),
  legend.key.size = unit(1, "cm"),
  axis.text = element_text(size = 20, family = "serif"),
  axis.title = element_text(size = 20, family = "serif")
  
  )

plot + guides(colour = guide_legend(override.aes = list(size=7))) + labs(color='Months') + scale_color_manual(values=group_col) 





```

#Matrices
```{r}




output = matrix(0, 371 * 12, 4)
output[,1] = 1:(371*12)
output[,3] = rep(1:12, 371)
output[,4] = rep(1:371, 12)

month_inds = seq(1, 371*12, 12)

mean_error_sym = numeric(371)

error_sym2 <- function(pred_v, actual_v){
  l = length(pred_v)
  out = numeric(l)
  
  for(i in 1:l){
    out[i] = error_sym(pred_v[i], actual_v[i])
  }
  return(mean(out))
}

c_m = matrix(0, 12, 12)


for(i in 1:371){
  ind = inds(i)
  test = lda_data[ind[1]:ind[2],]
  actuals = test$month
  preds = predict(lda_m, test)$class
  conf_matrix = confusionMatrix(actuals, preds)$table
  c_m = c_m + conf_matrix
  if(i == 100){
    first100_cm = round(c_m * 1/100)
    c_m = matrix(0, 12, 12)
  }
  if(i == 280){
    first280_cm = round(c_m * 1/100)
    c_m = matrix(0, 12, 12)
  }

  accs = class_error(actuals, preds)
  mean_error_sym[i] = mean(error_sym(as.numeric(preds), as.numeric(actuals)))
  # conf_m = confusionMatrix(preds, actuals)
  
  #output[month_inds[i]:(month_inds[i]+11),2] = conf_m$byClass[,11]
  #output[month_inds[i]:(month_inds[i]+11),2] =  accs = class_error(actuals, preds)
  
  out_p = numeric(12)
  for(j in 0:11){
    out_p[j+1] = mean(error_sym(as.numeric(preds[preds == j+1]), as.numeric(actuals[preds == j+1])))
  }
  output[month_inds[i]:(month_inds[i]+11),2] = out_p

}
last_cm = round(c_m * 1/(371-281))


```


#matrices2
```{r}
inds = seq(1,1332,1332/4)

interval_years = character(4)
years = data1$year
interval_years[1] = paste(years[inds[1]], " - ", years[inds[2]])
interval_years[2] = paste(years[inds[2]], " - ", years[inds[3]])
interval_years[3] = paste(years[inds[3]], " - ", years[inds[4]])
interval_years[4] = paste(years[inds[4]], " - ", years[1332])



confusion_boot <- function(dat, reps = 500, samples = 500){
  conf_matrix = matrix(0, 12, 12)
  for(i in 1:reps){
    inds = sample.int(length(dat), samples, replace = T)
    actuals = dat$month
    preds = predict(lda_m, dat)$class
    conf_matrix = conf_matrix + confusionMatrix(actuals, preds)$table
  }
  conf_matrix = conf_matrix * 1/reps
  return(conf_matrix)
}


confusion_list = list()
for(i in 1:4){
  index = (inds[i]:(inds[i] + 332))
  test = lda_data[index,]
  confusion_list[[i]] = confusion_boot(test, 1000, 1000)
}

to_percentage <- function(mat){
  for(i in 1:nrow(mat)){
    mat[i,] = (mat[i,] / sum(mat[i,])) * 100
  }
  return(round(mat,1))
}




```

#prep
```{r}
melted_list = list()

for(i in 1:4){
  melt_perc = melt(to_percentage(confusion_list[[i]]))
  melt_perc[,1] = factor(melt_perc[,1], labels = month_names)
  melt_perc[,2] = factor(melt_perc[,2], labels = month_names)
  melted_list[[i]] = melt_perc
}

```


#correlation matrices
```{r}
i = 1
for(i in 1:4){
  plot = ggplot(melted_list[[i]], aes(Prediction, Reference)) +
    coord_flip() +
    geom_tile(aes(fill = value), colour = "white") +
    scale_fill_gradient2(low = "white", high = "red", mid = "blue", 
     midpoint = 50, limit = c(0,100), space = "Lab", 
    name="Percentage per class")  +
    
    ggtitle(paste("Prediction percentages of time period", interval_years[i])) +
    geom_text(aes(Prediction, Reference, label = value), color = "black", size = 4) +
    labs(x = "",y = "") +
    theme_bw() +
    theme(
      #legend.title = element_blank(),
      plot.title = element_text(hjust = 0.5, family = "serif", size = 20),
      axis.text.x = element_text(angle=30,hjust=1,vjust=1.0, size = 20, family = "serif"),
      axis.text.y = element_text(size = 20, family = "serif"))
  print(plot)

 #coord_flip()
# Print the heatmap
#print(ggheatmap)

}




```


#lda boot
```{r}
i = 1

lda_boot <- function(i, reps = 500, samples = 500){
  #ind = inds(i)
  #reps = 500
  #samples  = 500
  test = lda_data[(i[1]:i[2]),]
  output_list_b = list()
  mean_errors_b = numeric(reps)
  mean_precision_b = numeric(reps)
  mean_errors_b_month = matrix(0, reps, 12)
  mean_precision_b_month = matrix(0, reps, 12)
  for(i in 1:reps){
    index = sample.int(length((ind[1]:ind[2])), samples, replace = T)
    test_b = test[index,]
    true_b = test_b$month
    predicted_b = predict(lda_m, test_b)$class
    mean_errors_b[i] = mean(error_sym(as.numeric(predicted_b), as.numeric(true_b)))
    out_p = numeric(12)
    out_precision = numeric(12)
    for(j in 0:11){
      out_p[j+1] = mean(error_sym(as.numeric(predicted_b[predicted_b == j+1]), as.numeric(true_b[predicted_b == j+1])))
      out_precision[j+1] = mean(as.numeric(predicted_b[predicted_b == j+1]) == as.numeric(true_b[predicted_b == j+1]))
    }
    mean_precision_b[i] = mean(out_precision)
    mean_precision_b_month[i,] = out_precision
    mean_errors_b_month[i,] = out_p
  }
  
  output_list_b$mean = mean(mean_errors_b, na.rm = T)
  quantiles = quantile(mean_errors_b, probs = c(0.025, 0.975), na.rm = T, type = 8)
  output_list_b$quantiles = quantiles
  output_list_b$month_mean = colMeans(mean_errors_b_month, na.rm = T)
  
  output_list_b$precision_means = colMeans(mean_precision_b_month)
  output_list_b$mean_precision = mean(mean_precision_b)
  output_list_b$quant_mean_precision = quantile(mean_precision_b, probs = c(0.025, 0.975), na.rm = T, type = 8)
  
  quants_months = matrix(0, 12, 2)
  quants_months_precision = matrix(0, 12, 2)
  for(i in 1:12){
    quants_months[i,] = quantile(mean_errors_b_month[,i], probs = c(0.025, 0.975), na.rm = T, type = 8)
    quants_months_precision[i,] = quantile(mean_precision_b_month[,i], probs = c(0.025, 0.975), na.rm = T, type = 8)
  }
  output_list_b$quantiles_precision_months = quants_months_precision
  output_list_b$quantils_months = quants_months
  return(output_list_b)
}




```


#average month error
```{r}

index_100 = seq(482, 1332, 100)
index_100[9] = 1332
year_index_100 =  1853 + (1/12 * index_100)

inds = round(seq(0, 111, 111/8)[4:9] * 12)
inds[1] = inds[1]+1

#df = data.frame(time = 1:371, mean_err = mean_error_sym)
error_means = numeric(6)
error_precision = numeric(6)
quant_error_means = matrix(0, 6, 2)
quant_error_means_pr = matrix(0, 6, 2)
month_list = list()
month_list2 = list()
for(j in 1:12){
  month_list[[j]] = c(1,1,1)
  month_list2[[j]] = c(1,1,1)
}
for(i in 1:6){
  print(i)
  #ind = index_100[i:(i+1)]
  ind = c((inds[i]-500),inds[i])
  result = lda_boot(ind, reps = 1000, samples = 300)
  error_precision[i] = result$mean_precision
  error_means[i] = result$mean
  quant_error_means[i,] = result$quantiles
  quant_error_means_pr[i,] = result$quant_mean_precision

  for(j in 1:12){
    month_list[[j]] = rbind(month_list[[j]],c(
                            result$month_mean[j], 
                            result$quantils_months[j,1],
                            result$quantils_months[j,2]))
    
    month_list2[[j]] = rbind(month_list2[[j]],c(
                            result$precision_means[j], 
                            result$quantiles_precision_months[j,1],
                            result$quantiles_precision_months[j,2]))
  }
}
```

#average precision error
```{r}
df = data.frame(
                #time = 1:8,
                time = round(1853 + ((inds-250) * 1/12)),
                mean_err = error_means, 
                quant_min = quant_error_means[,1],
                quant_max = quant_error_means[,2])


plot = ggplot(data=df, aes(x = time, y = mean_err)) +
  geom_ribbon(aes(ymin=quant_min,ymax=quant_max),alpha=0.2) +
  geom_line() +
  geom_point(size = 4) +
  ylim(c(0,0.5)) +
  ylab("Symmetry error") +
  xlab("Time") +
  ggtitle("Average Symmetry error bootstrapped") +
  #geom_errorbar(aes(ymin=quant_min, ymax=quant_max), width=1) +
  
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, family = "serif", size = 15))
  theme_bw()+
  theme(axis.text.x = element_text(family = "serif", size = 25), 
        plot.title = element_text(hjust = 0.5, family = "serif", size = 20),
        axis.text.y = element_text(family = "serif", size = 15),
        #legend.position = "none", 
        axis.title.x = element_text(family = "serif", size = 25), 
        axis.title.y = element_text(family = "serif", size = 15),
        legend.key.size = unit(2, 'cm'),
        legend.title = element_text(family = "serif", size = 20),
        legend.text = element_text(family = "serif", size = 20))
  
print(plot)
```

#Symmetry error per month
```{r}
for(j in 1:12){
  df = data.frame(
                #time = 1:8, 
                #time = year_index_100[-9],
                time = round(1853 + ((inds-250) * 1/12)),
                mean_err = month_list[[j]][-1,1], 
                quant_min = month_list[[j]][-1,2],
                quant_max = month_list[[j]][-1,3])
  
  
    plots = ggplot(data=df, aes(x = time, y = mean_err)) +
    geom_ribbon(aes(ymin=quant_min,ymax=quant_max),alpha=0.2, col = palette[j]) +
    geom_line() +
    geom_point(col = palette[j], size = 4) +
    ylim(c(0,1.3)) +
    ylab("Symmetry error") +
    xlab("Time") +
    #geom_errorbar(aes(ymin=quant_min, ymax=quant_max), width=.3) +
    theme_bw() +
    ggtitle(paste("Symmetry error bootstrapped ", month_names[j], sep = "")) +
    theme(axis.text.x = element_text(family = "serif", size = 25), 
        plot.title = element_text(hjust = 0.5, family = "serif", size = 20),
        axis.text.y = element_text(family = "serif", size = 15),
        legend.position = "none", 
        axis.title.x = element_text(family = "serif", size = 25), 
        axis.title.y = element_text(family = "serif", size = 15),
        legend.key.size = unit(2, 'cm'),
        legend.title = element_text(family = "serif", size = 20),
        legend.text = element_text(family = "serif", size = 20))
    
  print(plots)
  ggsave(filename = paste("sym_err_", month_names[j], ".pdf", sep = ""),
         plot = last_plot(),
         width = 12,
         height = 8)


}
```

#Precision
```{r}
df = data.frame(
                #time = 1:8,
                time = round(1853 + ((inds-250) * 1/12)),
                mean_err = error_precision, 
                quant_min = quant_error_means_pr[,1],
                quant_max = quant_error_means_pr[,2])


plot = ggplot(data=df, aes(x = time, y = mean_err)) +
  geom_ribbon(aes(ymin=quant_min,ymax=quant_max),alpha=0.2) +
  geom_line() +
  geom_point(size = 4) +
  ylim(c(0.75,1)) +
  ylab("Precision") +
  xlab("Time") +
  ggtitle("Average Precision error bootstrapped") +
  theme_bw() +
  #geom_errorbar(aes(ymin=quant_min, ymax=quant_max), width=1) +
  
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, family = "serif", size = 15)) 
  theme(axis.text.x = element_text(family = "serif", size = 25), 
        plot.title = element_text(hjust = 0.5, family = "serif", size = 20),
        axis.text.y = element_text(family = "serif", size = 15),
        #legend.position = "none", 
        axis.title.x = element_text(family = "serif", size = 25), 
        axis.title.y = element_text(family = "serif", size = 15),
        legend.key.size = unit(2, 'cm'),
        legend.title = element_text(family = "serif", size = 20),
        legend.text = element_text(family = "serif", size = 20))
  
print(plot)
```

#precision per month
```{r}
for(j in 1:12){
  df = data.frame(
                #time = 1:8, 
                #time = year_index_100[-9],
                time = round(1853 + ((inds-250) * 1/12)),
                mean_err = month_list2[[j]][-1,1], 
                quant_min = month_list2[[j]][-1,2],
                quant_max = month_list2[[j]][-1,3])
  
  
    plot = ggplot(data=df, aes(x = time, y = mean_err)) +
    geom_ribbon(aes(ymin=quant_min,ymax=quant_max),alpha=0.2, col = palette[j]) +
    geom_line() +
    geom_point(col = palette[j], size = 4) +
    ylim(c(0.25,1)) +
    ylab("Precision error") +
    xlab("Time") +
    #geom_errorbar(aes(ymin=quant_min, ymax=quant_max), width=.3) +
    theme_bw() +
    ggtitle(paste("Precision bootstrapped ", month_names[j], sep = "")) +
    theme(axis.text.x = element_text(family = "serif", size = 25), 
        plot.title = element_text(hjust = 0.5, family = "serif", size = 20),
        axis.text.y = element_text(family = "serif", size = 15),
        legend.position = "none", 
        axis.title.x = element_text(family = "serif", size = 25), 
        axis.title.y = element_text(family = "serif", size = 15),
        legend.key.size = unit(2, 'cm'),
        legend.title = element_text(family = "serif", size = 20),
        legend.text = element_text(family = "serif", size = 20))
    
  print(plot)
  ggsave(filename = paste("precision_", month_names[j], ".pdf", sep = ""),
         plot = last_plot(),
         width = 12,
         height = 8)
}
```


